---
title: "Clinic"
output:
  html_notebook: default
  pdf_document: default
---

Drawing samples using an empirical cumulative density function of patient arrival times relative to their scheduled appointment.
```{r}
ecdf <- read.csv("arrivals.csv")
draw_sample_from_ecdf <-function(ecdf,n){
  l<-c()
  for (i in 1:n){
    l<-c(l,ecdf[ecdf$Num/100 == round(runif(1),2),]$CDF)
  }
  return (l)
}
list_sample <- draw_sample_from_ecdf(ecdf,10000)
list_sample <- list_sample/60
write.table(list_sample, "sample.txt", append = FALSE, sep = " ", dec = ".",row.names = FALSE, col.names = FALSE)
```

Walk-in patients inter-arrival times.
```{r}
totsum = 0
for(i in 1:10000){
  # 5 patients per day, 9 hour workday 
  totsum = totsum + sum(rexp(5,rate = 5/(60*9)))
}
#It should sum up to 9*60
print(totsum/10000)
```

Appointment length - min = 15, mean = 18, and max = 30.
```{r}
mean(Filter(function(x) x < 30, rgamma(15000, shape = 1, scale = 3) + 15)[1:10000])
```
Pharmacy(~300 pharmacy walk-in pickups each day) - inter-arrival times:
```{r}
totsum = 0
for(i in 1:10000){
  # 300 walk-ins per day, 24 hour workday 
  totsum = totsum + sum(rexp(300,rate = 300/(60*24)))
}
#It should sum up to 24*60
print(totsum/10000)
```
Time to fill a perscription(strongly right-skewed distribution with a mean time of ~5 minutes and a maximum time of ~15 minutes):
```{r}
mean(Filter(function(x) x < 15, rgamma(15000, shape = 1, scale = 2) + 3)[1:10000])
```
Radiology(~220 walk-ins per day) - inter-arrival times:
```{r}
totsum = 0
for(i in 1:10000){
  # 300 walk-ins per day, 24 hour workday 
  totsum = totsum + sum(rexp(300,rate = 300/(60*9)))
}
#It should sum up to 9*60
print(totsum/10000)
```
Radiology Procedure Times
```{r}
radio_ecdf <- read.csv("radio.csv")
names(radio_ecdf) = c("Num","CDF")
list_sample <- draw_sample_from_ecdf(radio_ecdf,10000)
list_sample <- list_sample/60
write.table(list_sample, "sample_radio.txt", append = FALSE, sep = " ", dec = ".",row.names = FALSE, col.names = FALSE)
```

Lab(~350-400 walk-ins per day) - inter-arrival times:
```{r}
totsum = 0
for(i in 1:10000){
  # 300 walk-ins per day, 9 hour workday 
  totsum = totsum + sum(rexp(375,rate = 375/(60*24)))
}
#It should sum up to 24*60
print(totsum/10000)
```
Lab visit length(min = 3, mean = 7-8, max = 15)
```{r}
mean(Filter(function(x) x < 15, rgamma(15000, shape = 2, scale = 2.5) + 3)[1:10000])
```
Reading/transforming data
```{r}
doc_schedule <- read.csv('doc_sched.csv')
doc_schedule$date <- as.Date(doc_schedule$slot_begin_time, format = "%m/%d")
doc_schedule$date2 <- strptime(doc_schedule$slot_begin_time, "%m/%d/%y %H:%M")
doc_schedule$hm <- format(doc_schedule$date2, "%H:%M")   
```

Schedules
```{r}
print_doc_sched<-function(doc_schedule, n){
  doc_sched<- doc_schedule[doc_schedule$doc_id == n, ]
  lab <- with(df, paste(format(doc_sched$date2, "%H"), format(doc_sched$date2, "%M"), sep = ":"))
  gg <- ggplot(data = doc_sched, aes(x = date, y = hm, fill = supp_block)) +
  geom_tile(colour = "grey50") + scale_y_discrete(breaks = lab)
  print(gg)
}
#Doctor 1
print_doc_sched(doc_schedule,1)
```
Actual schedules 
```{r}
print_doc_act_sched<-function(doc_schedule, n){
  doc_sched<- doc_schedule[doc_schedule$doc_id == n, ]
  lab <- with(df, paste(format(doc_sched$date2, "%H"), format(doc_sched$date2, "%M"), sep = ":"))
  gg <- ggplot(data = doc_sched, aes(x = date, y = hm, fill = appt_block)) +
  geom_tile(colour = "grey50") + scale_y_discrete(breaks = lab)
  print(gg)
}
#Doctor 1
print_doc_act_sched(doc_schedule,1)
```

Fill rates & no-show rates
```{r}
app_type <- unique(doc_schedule$appt_block)
app_type <- app_type[app_type!='UNUSED']
app_combos <- unique(doc_schedule$supp_block)
unique_dates <- unique(doc_schedule$date)
dayoftheweek <- weekdays(unique_dates)
names(dayoftheweek) <- unique_dates

fill_rate_func <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED')/sum(doc_schedule$supp_block == type))
}
no_show_rate_func <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$seen == 0 )/sum(doc_schedule$supp_block == type))
}
fill_rate <- sapply(app_combos, fill_rate_func)
no_show_rate <- sapply(app_combos, no_show_rate_func)
```

Fill rates & no-show rates by day of week
```{r}
workdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
fill_rates_by_weekday <- vector("list", 5)
no_show_rates_by_weekday <- vector("list", 5)
for(i in 1:5){
  fill_rates_by_weekday[[i]] <- matrix(NA, nrow = 21, ncol = 13)
  no_show_rates_by_weekday[[i]] <- matrix(NA, nrow = 21, ncol = 13)
}
for(i in 1:5){
  for(j in 1:21){
    for(k in 1:13){
    total_possible <- sum(doc_schedule$supp_block == app_combos[k] & doc_schedule$doc_id == j-1 & dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] )
    total_used <- sum(doc_schedule$supp_block == app_combos[k] & doc_schedule$appt_block != 'UNUSED' & dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] & doc_schedule$doc_id == j-1)
    total_no_show <- sum(doc_schedule$supp_block == app_combos[k] & doc_schedule$seen == 0 & dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] & doc_schedule$doc_id == j-1)
    fill_rates_by_weekday[[i]][j,k] = total_used/total_possible
    no_show_rates_by_weekday[[i]][j,k] = total_no_show / total_possible
    }
  }
}

```

Fill rates morning(am) shift and afternoon(pm) shift
```{r}
fill_rate_func_am <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED' & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))/sum(doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M")) )
}
fill_rate_func_pm <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED' & strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))/sum(doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M")) )
}
pm_fill_rates <- sapply(app_combos, fill_rate_func_pm)
names(pm_fill_rates) <- app_combos
am_fill_rates <- sapply(app_combos, fill_rate_func_am)
names(am_fill_rates) <- app_combos
print(am_fill_rates)
print(pm_fill_rates)
```

No-show rates morning(am) shift and afternoon(pm) shift
```{r}
no_show_rate_func_am <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED'& doc_schedule$seen == 0 & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))/sum(doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M")) )
}
no_show_rate_func_pm <-function(type){
  return(sum(doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED' & doc_schedule$seen == 0 &strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))/sum(doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M")) )
}

pm_no_show_rates <- sapply(app_combos, no_show_rate_func_pm)
names(pm_no_show_rates) <- app_combos

am_no_show_rates <- sapply(app_combos, no_show_rate_func_am)
names(am_no_show_rates) <- app_combos
print(am_no_show_rates)
print(pm_no_show_rates)
```

No-show rates morning(am) shift and afternoon(pm) shift by day of the week
```{r}
no_show_rate_func_am_w <-function(type, i =4){
  return(sum(dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] &doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED'& doc_schedule$seen == 0 & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))/sum(dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] & doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M")) )
}
no_show_rate_func_pm_w <-function(type, i =4){
   return(sum(dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] &doc_schedule$supp_block == type & doc_schedule$appt_block != 'UNUSED'& doc_schedule$seen == 0 & strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))/sum(dayoftheweek[as.character(doc_schedule$date)]  == workdays[i] & doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M")) )
}
am_no_show_rates_mon <- sapply(app_combos, no_show_rate_func_am_w)
names(am_no_show_rates_mon) <- app_combos
pm_no_show_rates_mon <- sapply(app_combos, no_show_rate_func_pm_w)
names(pm_no_show_rates_mon) <- app_combos

am_no_show_rates_tue <- sapply(app_combos, no_show_rate_func_am_w)
names(am_no_show_rates_tue) <- app_combos
pm_no_show_rates_tue <- sapply(app_combos, no_show_rate_func_pm_w)
names(pm_no_show_rates_tue) <- app_combos

am_no_show_rates_wed <- sapply(app_combos, no_show_rate_func_am_w)
names(am_no_show_rates_wed) <- app_combos
pm_no_show_rates_wed <- sapply(app_combos, no_show_rate_func_pm_w)
names(pm_no_show_rates_wed) <- app_combos

am_no_show_rates_thu <- sapply(app_combos, no_show_rate_func_am_w)
names(am_no_show_rates_thu) <- app_combos
pm_no_show_rates_thu <- sapply(app_combos, no_show_rate_func_pm_w)
names(pm_no_show_rates_thu) <- app_combos

am_no_show_rates_fri <- sapply(app_combos, no_show_rate_func_am_w)
names(am_no_show_rates_fri) <- app_combos
pm_no_show_rates_fri <- sapply(app_combos, no_show_rate_func_pm_w)
names(pm_no_show_rates_fri) <- app_combos
```
When two appt types can be booked for a slot, which is more likely to be booked(am/pm)
```{r}
more_likely_func <-function(type){
    app_type1 <- sapply(strsplit(as.character(type), "/"), "[", 1)
    app_type2 <- sapply(strsplit(as.character(type), "/"), "[", 2)
    if(grepl("SD", type)){
      app_type1 <- sapply(strsplit(app_type1, " SD"), "[", 1)
      app_type2 <- sapply(strsplit(app_type2, " SD"), "[", 1)
      if(app_type2 == "VIDEO"){
        app_type2 <- "VIDEO VISIT"
      }
    }
    total <- sum(doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type)
    type1 <- sum(doc_schedule$appt_block == app_type1 & doc_schedule$supp_block == type)
    type2 <- sum(doc_schedule$appt_block == app_type2 & doc_schedule$supp_block == type)
    return(c(type1/total, type2/total))
}
more_likely_func_am <-function(type){
    app_type1 <- sapply(strsplit(as.character(type), "/"), "[", 1)
    app_type2 <- sapply(strsplit(as.character(type), "/"), "[", 2)
    if(grepl("SD", type)){
      app_type1 <- sapply(strsplit(app_type1, " SD"), "[", 1)
      app_type2 <- sapply(strsplit(app_type2, " SD"), "[", 1)
      if(app_type2 == "VIDEO"){
        app_type2 <- "VIDEO VISIT"
      }
    }
    total <- sum(doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))
    type1 <- sum(doc_schedule$appt_block == app_type1 & doc_schedule$supp_block == type & strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))
    type2 <- sum(doc_schedule$appt_block == app_type2 & doc_schedule$supp_block == type&strptime(doc_schedule$hm, format = "%H:%M") < strptime("12:30", format = "%H:%M"))
    return(c(type1/total, type2/total))
}
more_likely_func_pm <-function(type){
    app_type1 <- sapply(strsplit(as.character(type), "/"), "[", 1)
    app_type2 <- sapply(strsplit(as.character(type), "/"), "[", 2)
    if(grepl("SD", type)){
      app_type1 <- sapply(strsplit(app_type1, " SD"), "[", 1)
      app_type2 <- sapply(strsplit(app_type2, " SD"), "[", 1)
      if(app_type2 == "VIDEO"){
        app_type2 <- "VIDEO VISIT"
      }
    }
    total <- sum(doc_schedule$appt_block != 'UNUSED' & doc_schedule$supp_block == type &strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))
    type1 <- sum(doc_schedule$appt_block == app_type1 & doc_schedule$supp_block == type&strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))
    type2 <- sum(doc_schedule$appt_block == app_type2 & doc_schedule$supp_block == type&strptime(doc_schedule$hm, format = "%H:%M") > strptime("12:30", format = "%H:%M"))
    return(c(type1/total, type2/total))
}
print(app_combos[grepl("/", app_combos) & app_combos != "PCP/OVBK PCP"])
more_likely <- sapply(app_combos[grepl("/", app_combos) & app_combos != "PCP/OVBK PCP"], more_likely_func)
print(more_likely)
more_likely_am <- sapply(app_combos[grepl("/", app_combos) & app_combos != "PCP/OVBK PCP"], more_likely_func_am)
print(more_likely_am)
more_likely_pm <- sapply(app_combos[grepl("/", app_combos) & app_combos != "PCP/OVBK PCP"], more_likely_func_pm)
print(more_likely_pm)
```